Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
paper final draft

We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm`.[To be updated...]

@@

## Days to Election (Recency) Effet

@@

## Poster Effec Analysis

```{r}

@@

```{r}

>>>>

@@

## Days to Election (Recency) Effect

@@

```{r}
#| label: fig-candidate_fixed
#| fig-cap: "Candidate Fixed Effects in Hierachical Bayesian Model" 
#| echo: false
#| warning: false
#| message: false

# Load necessary libraries
library(ggplot2)
library(readr)
library(here)

# Load the candidate fixed effect data
candidate_data <- read_csv(here("data", "02-analysis_data", "candidate_fixed_effect.csv"))

# Plot candidate fixed effects
ggplot(candidate_data, aes(x = reorder(candidate_name, gamma_k), y = gamma_k)) +
  geom_point(color = "blue", size = 3) +
  geom_errorbar(aes(ymin = gamma_k - 0.1, ymax = gamma_k + 0.1), width = 0.2) + # Adjust error if data available
  coord_flip() +
  labs(
    x = "Candidate",
    y = "Fixed Effect Estimate (gamma_k)"
  ) +
  theme_minimal()

@@

@fig-candidate_fixed illustrates the candidate fixed effect estimates for various candidates in this Hierarchical Bayesian Model, which predicts outcomes in the context of the 2024 U.S. presidential election. While this paper only focuses on Trump and Harris, in this plot each point represents the fixed effect estimate for a candidate, with higher values indicating a stronger predicted effect within the model. The plot orders candidates by their fixed effect, allowing for a visual comparison of the relative influence attributed to each candidate. Candidates at the top of the plot, such as those with fixed effects above 40, are projected to have a more substantial impact within the model, while candidates with lower fixed effects are likely to have a minimal effect on the outcome. This visualization helps to convey the variation in candidate influence as determined by our modeling approach.
